
\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{url}									
%%https://www.overleaf.com/project/5f23d7ea8109fa0001d3b23f


\title{AmatoCV}
\author{Amato Pierluigi}
\date{May 2020}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Pierluigi Amato}
\cvpersonalinfo{
%Via Caduti Lyra 41, 63, Navacchio, Cascina (PI), Toscana, \cvinfosep 
Cascina (PI), Tuscany, Italy\cvinfosep 
04/07/1987 \cvinfosep 
+39 3285822051\cvinfosep
amato.pierluigi@gmail.com\cvinfosep\href{https://www.linkedin.com/in/pierluigi-amato-b219ab45}{\faLinkedinSquare}
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Summary}
Enthusiastic and dedicated Software Engineer with a solid background in real-time programming, Linux operating systems, and communication protocols. Throughout my career, I've developed a range of solutions—from web applications to real-time systems for communication between microservices and on-premise software.

I honed my skills working as a Software Engineer Consultant at Leonardo in La Spezia, using C, C++, Matlab, and Python. Later, I spent time developing software for 6-DOF Robots (Kawasaki, Fanuc), where I designed a core framework integrating MySql, Halcon, and OPC technologies.

\textbf{Currently}, I work at Fincantieri NexTech in the maritime industry. I am heavily focused on the design and development of a C\#-based ecosystem of applications dedicated to the automation management of modern ships. Working alongside a talented team of engineers, I am also implementing an advanced SCADA system designed to enable future ships to travel with robust, cybersecurity-aware systems. \textbf{\href{https://giga487.github.io/AmatoSplashPage/}{GitHub Page}}

\section{Jobs}
\begin{itemize}
\item \textbf{Software Engineer, Fincantieri NexTech Pisa, 2/24-now}
\begin{itemize}
    \item Web Application with Blazor Web Assembly, Web Server, MVVM
    \item Asp .net core API
    \item grpc, https, managing heavy data flow.
    \item developing with blazor and C\#, in the .net core 8-9
    \item using Unit test tools for testing.
    \item advanced analysis, testing and implementation of a real-time SCADA system.
    \item Design pattern and Documentation.
    \item OPC-UA, OPC-DA and ABB Plc's environment
    \item custom in-memory database (IMDB) for real-time dispatch of data in C\#
\end{itemize}

\item \textbf{Robotics and Automation Engineer, Robot System Automation, 08/22-01/24}
\begin{itemize}
    \item \href{https://skia.org/}{SKIA 2D graphics}, used for custom USER INTERFACE
    \item Matlab and Simulink for testing with hardware in the loop.
    \item Desktop Application in C\# for Integration with Robot
    \item Company Software Version Manager (\textbf{GITHUB})
    \item C\#, Custom Vision system with open Go Pro
    \item Develop in C\# .framework 4.8.1, Entity Framework, Polymorphism, Modbus PLC, Design Patterns: Builder, State, Observer
    \item Custom Keyboard in C\# .framework 4.8.1, Windows API.
    \item \href{https://www.mvtec.com/products/halcon}{Halcon} Vision integration and pattern recognition for custom Scanner in C\#, WPF in .net framework 4.8, XAML. 
    \item C\# Server with OPC-UA Protocol.
    \item Asp .net core API
\end{itemize}

\item \textbf{Software Test Engineer, Akka technologies, at Mermec, AngelStar Company, San Piero a Grado (PI), Railway System, 09/21-08/22:}
\begin{itemize}
\item Develop of Python log parser, OOP
\end{itemize}
\item \textbf{Software Engineer, Akka technologies, at Leonardo, La Spezia, Defensive Naval Systems, 2019-9/2021:}
\begin{itemize}
    \item Develop of features for Real-time Operating System, Debug, log Analysis, Integrity Tests and Unit Tests
    \item TCP-IP, UDP sockets
    \item Mil-Std 498 Documents
    \item Porting to UNIX, Linux and Windows
    \item LabWindows/CVI
    \item Customer logistic supports
    \item Windows Provisioning (Power-Shell) and Unix bash scripts
    \item Utilities software in C++ (QT) and C\# console application.
\end{itemize}
\item \textbf{Talentika (Start-up) in Rosignano Solvay, 2018-2019}
\end{itemize}
 
\section{Education}

\begin{itemize}
\item M.Sc, University of Pisa, Mechatronics Engineering, 2015-2019, link to the relative article: \href{https://ieeexplore.ieee.org/document/10016730}{here}

\item Engineering professional qualification 
\end{itemize}

\section{Technical Skills}

\begin{itemize}
\item \textbf{Tools:}MatLab and Simulink, Git, Visual studio: Profiling, Unit Test, Integrity Test
\item \textbf{Sistemi operativi:} OS UNIX, real-time
\item \textbf{Programming languages:} C, C++, Python, C$\#$ 
\item \textbf{Qt:} Qt Gui, MVC and design pattern. 
\item \textbf{Cad 3d:} SolidWorks
\item \textbf{Lab Tools}
\end{itemize}
 
\section{Projects}
\begin{itemize}
\item On my \textbf{GitHub} 
\href{https://github.com/giga487}{\faGithub}
\item \textbf{RR planar joint, CASADI}
Searching for an optimal solution, Casadi. Python 
\item \textbf{Standford Manipulator Control}

\item \textbf{Unity game development:}
\begin{itemize}
\item Working on a Unity3D Game, using Physics
\item Backend analysis tools, python, typescript
\item New Physics design, new ballistic for gaming design
\end{itemize}

\item \textbf{Ultima Online free server:}
develop of massive multiplayer game, for fun project, actually active.
\begin{itemize}
\item TCP/IP Client/Server custom communication
\item Design and implementation of new features such as automated game events with match-making and simple AI
\item C\# expert, Design Patterns, Events, Async, Await, Multi-threading
\item ServUO (backend) Linux porting for MONO
\item Database and Discord Rest API's
\item Multiplayer C\# OOP oriented to optimization, hash map, dictionaries and list
\item Develop on ClassicUO (custom game client) with XNA graphics engine
\item Unit test and Integrity test using Visual Studio 2022
\item Debugging, Profiling and performance testing using Visual Studio 2022

\end{itemize}



\end{itemize}

\cvsubsection{Master Thesis}[SSSUP]
\begin{itemize}
    \item \textbf{Improving GNSS-Free train localization by integrating odometry with inertial data and track information.}
    \newline
In collaboration with Ansaldo-Hitachi and Scuola Superiore Sant’Anna, I’ve studied and developed a method for the GNSS-Free localization of a railway system by analyzing the characteristics of the route and the dynamics of the train. A \textbf{railway simulator} with dynamics, control and a set of tools for the analysis of real data have been developed. 

\end{itemize}

\cvsubsection{Projects}[Pisa University, MS Mechatronics]
\begin{itemize}
\item \textbf{Inverted pendulum with inertial wheel}

Designing, simulating and constructing an inverse pendulum with inertial wheels. Generating the control system, using Python to test the effectiveness of the IMU as well as using OPEN GL and Multi-thread: \href{https://www.youtube.com/watch?v=wL0Aum5eXEo}{\faYoutube}

\item \textbf{Indoor Localization} Designing a set of Embedded systems on Arm M4 using an Ultra Wide Band antenna. The systems used triangulation to locate a drone within an area not covered by GPS signal.
\item \textbf{Real-time} Designing and developing a videogame with hard-real time problems. Process analysis of a real-time system with Allegro graphic tools. 
\item \textbf{Haptic Manipulation} Studying, analysing and controlling a haptic manipulator, using QT libraries. The device supplied lacked a user interface and a control system.
\item \textbf{Path Planning} Developing a path planning control for an airplane. 
\item \textbf{Robust Control} Controlling of an uncertain systems with H-inf, H-2, $\mu$ using Matlab. Control of fully actuated, not linear for an Handle Robots.
\end{itemize}
\cvsubsection{Bechelor's Degree}[Pisa University, Electronic Engineer]

\begin{itemize}
\item \textbf{Progetto e realizzazione di una scheda per misure acustiche PV orientate a funzioni di localizzazione}

Design and Analysis of an electronic system for the study of audiometric sources using PV sensors.

\end{itemize}

 \section{Other Skills}
\begin{description}[widest=Langauges]
\item[Software] MatLab, SolidWorks, Eclipse (Ide), Operating systems
\item[Languages]	English: B1+ CLI, Pisa University
\item[LATEX] This document in writed in \LaTeX
\end{description}


\end{document}
